### 2014-03-20 LaTeX/RhodiumLit.tex
Added inflation

>>>>

\cite{imai:weinstein:2000} explored the differing economic impacts of civil war by distinguinshing between those conflicts cover larger or smaller geographic areas.  Using a pooled OLS regression, they find that there is a negative correlation between geographical spread and the decade average of economic growth for each country.  However, in subsequent simulations that account for estimation and fundamental uncertainty,
